Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-04-17 paper/paper.tex
PDF Info
Semicolon

@@

The \emph{association graph encoding} of a subgraph isomorphism problem (illustrated in
\cref{figure:sip}) is constructed by creating a new graph with a vertex for each pair $(p, t)$ of
vertices from the pattern and target graphs respectively. There is an edge between vertex $(p_1,
t_1)$ and vertex $(p_2, t_2)$ if mapping $p_1$ to $t_1$ and $p_2$ to $t_2$ simultaneously is
permitted, i.e.\ $p_1$ is adjacent to $p_2$ if and only if $t_1$ is adjacent to $t_2$. A clique of
size equal to the order of the pattern graph exists in the association graph if and only if the
problem is satisfiable \citep{Levi:1973}. We used this encoding with the BBMC clique algorithm
\citep{SanSegundo:2011}, which we implemented in C++. Usually BBMC solves the optimisation version
of the clique problem, we adapted it to solve the decision problem by initialising the incumbent to
be one less than the decision value, and allowing it to exit as soon as a clique with size equal to
the decision value is encountered.  Again, our results show that the instances in the central region
remain hard, and additionally, some of the easy unsatisfiable instances become hard.

>>>>

\pdfinfo{
    /Title (Heuristics and Really Hard Instances for Subgraph Isomorphism Problems)
    /Author (Ciaran McCreesh, Patrick Prosser, James Trimble)
}

@@

The \emph{association graph encoding} of a subgraph isomorphism problem (illustrated in
\cref{figure:sip}) is constructed by creating a new graph with a vertex for each pair $(p, t)$ of
vertices from the pattern and target graphs respectively. There is an edge between vertex $(p_1,
t_1)$ and vertex $(p_2, t_2)$ if mapping $p_1$ to $t_1$ and $p_2$ to $t_2$ simultaneously is
permitted, i.e.\ $p_1$ is adjacent to $p_2$ if and only if $t_1$ is adjacent to $t_2$. A clique of
size equal to the order of the pattern graph exists in the association graph if and only if the
problem is satisfiable \citep{Levi:1973}. We used this encoding with the BBMC clique algorithm
\citep{SanSegundo:2011}, which we implemented in C++. Usually BBMC solves the optimisation version
of the clique problem; we adapted it to solve the decision problem by initialising the incumbent to
be one less than the decision value, and allowing it to exit as soon as a clique with size equal to
the decision value is encountered.  Again, our results show that the instances in the central region
remain hard, and additionally, some of the easy unsatisfiable instances become hard.
